Software Frameworks for Parallel Deep Learning

### 2016-07-28 report/Report/para/2-comparison.tex
reorganized section and subsection layout

\section{Framework Comparison}
\begin{table*}
\centering
\caption{Open-source Frameworks}
\begin{tabular}{|m{2.6cm}<{\centering}|m{2cm}<{\centering}|m{2cm}<{\centering}|m{2cm}<{\centering}|m{2cm}<{\centering}|m{2cm}<{\centering}|m{2cm}<{\centering}|}
\hline
Platform & Tensorflow & CNTK & Deeplearning4j & MXNet & H2O & CaffeOnSpark\\ \hline\hline
Release Date & 2016 & 2016 & 2015 & 2015 & 2014 & 2016\\
\hline
Core Language & C++  & C++ & Java  & C++ & Java &C++, Scala\\
\hline
API & C++, Python & NDL & Java, Scala & C++, Python, R, Scala, Matlab, Javascript, Go, Julia & Java, R, Python, Scala, Javascript, web-UI & Python, Matlab, Scala\\
\hline
Computation Model & Sync or async & Sync & Sync & Sync or async & Async & Sync\\
\hline
Communication Model & Parameter server & MPI & Iterative MapReduce & Parameter server & Distributed fork-join & MPI Allreduce\\
\hline
Data Parallelism & \cmark & \cmark & \cmark & \cmark& \cmark & \cmark \\
\hline
Model Parallelism & \cmark & N/A & \xmark & \cmark & \xmark & \xmark\\
\hline
Programming Paradigm & Imperative & Imperative & Declarative & Both & Declarative & Declarative\\
\hline
Fault Tolerance & Checkpoint-and-recovery & Checkpoint-and-resume & Checkpoint-and-resume & Checkpoint-and-resume & N/A & N/A\\
\hline
Visualization & Graph-visualization (interactive), training monitoring & Graph visualization (static) & Training monitoring & None & None & Summary Statistics\\
\hline
\end{tabular}
\end{table*}

The relevance of release date, core language, user-facing APIs are self-explanatory. Computation model specifies the nature of data consistency through execution, i.e. whether updates are synchronous or asynchronous. In context of optimization kernels like stochastic gradient descent (SGD), synchronous execution has better convergence guarantees by maintaining consistency or near-consistency with sequential execution. However, asynchronous SGD can exploit more parallelism and train faster, but with less guarantees of convergence speed. Note that frameworks like Tensorflow and MXNet simply leave this as a tradeoff choice for the user.

@@

>>>>

\section{Framework Comparison}
\begin{table*}
\small
\centering
\caption{Open-source Frameworks}
\resizebox{\textwidth}{!}{
    \begin{tabular}{|m{2cm}<{\centering}|m{1.5cm}<{\centering}|m{1.5cm}<{\centering}|m{2cm}<{\centering}|m{1.5cm}<{\centering}|m{1.5cm}<{\centering}|m{1.7cm}<{\centering}|m{1.5cm}<{\centering}|m{1.5cm}<{\centering}|}
    \hline
    Platform & Tensorflow & CNTK & Deeplearning4j & MXNet & H2O & CaffeOnSpark & Theano & Torch \\ \hline\hline
    Release Date & 2016 & 2016 & 2015 & 2015 & 2014 & 2016 & 2010 & 2011 (deep learning) \\
    \hline
    Core Language & C++  & C++ & Java  & C++ & Java & C++, Scala & C++ & C \\
    \hline
    API & C++, Python & NDL & Java, Scala & C++, Python, R, Scala, Matlab, Javascript, Go, Julia & Java, R, Python, Scala, Javascript, web-UI & Python, Matlab, Scala & Python & Lua \\
    \hline
    Synchronization Model & Sync or async & Sync & Sync & Sync or async & Async & Sync & Async & Sync \\
    \hline
    Communication Model & Parameter server & MPI & Iterative MapReduce & Parameter server & Distributed fork-join & MPI Allreduce & N/A & N/A \\
    \hline
    Multi-GPU & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark \\
    \hline 
    Multi-node & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \xmark & \xmark \\
    \hline
    Data Parallelism & \cmark & \cmark & \cmark & \cmark& \cmark & \cmark & \cmark & \cmark \\
    \hline
    Model Parallelism & \cmark & N/A & \xmark & \cmark & \xmark & \xmark & \cmark & \cmark \\
    \hline
    Programming Paradigm & Imperative & Imperative & Declarative & Both & Declarative & Declarative & Imperative & Imperative \\
    \hline
    Fault Tolerance & Checkpoint-and-recovery & Checkpoint-and-resume & Checkpoint-and-resume & Checkpoint-and-resume & N/A & N/A & Checkpoint-and-resume & Checkpoint-and-resume \\
    \hline
    Visualization & Graph (interactive), training monitoring & Graph (static) & Training monitoring & None & None & Summary Statistics & Graph (static) & Plots \\
    \hline
    \end{tabular}
}
\end{table*}

The relevance of release date, core language, user-facing APIs are self-explanatory. Synchronization model specifies the nature of data consistency through execution, i.e. whether updates are synchronous or asynchronous. In context of optimization kernels like stochastic gradient descent (SGD), synchronous execution has better convergence guarantees by maintaining consistency or near-consistency with sequential execution. Asynchronous SGD can exploit more parallelism and train faster, but with less guarantees of convergence speed. Frameworks like Tensorflow and MXNet leave this tradeoff as a choice to the user.

@@

There are three possible levels of parallelism at the hardware level: cores within a CPU/GPU device, across multiple devices (usually GPUs for deep learning), or across machines. Most lower-level library kernels (e.g. for linear algebra) are designed to use multiple cores of a device by default, so this is not a major point of comparison. At this point, all the frameworks also support parallelism across multiple GPUs. Theano and Torch do not yet support multi-machine parallelism.
